\documentclass[english]{uspatent}
\begin{document}

%% Assignee INFO
\setAssigneeName{Assignee Name}
\setAssigneeAddress{Assignee Address}
\setAssigneeCity{Assignee City, State, Zip}
\setAssigneePhone{Assignee Phone}
%% Docket Number
\setDocketNumber{Docket Number}
%% Other Inventor INFO
\setOtherInventor{Another Inventor}
\setOtherInventor{Yet Another Inventor}
%% Version
\setDocumentVersion{0.1.0}
%% Set Printing Mode (one is Application mode and another one is draft mode)
%\setPrintingModeApplication
\setPrintingModeDraft

\include{Drawings}

\title{Radio Telescope diftributed system}
\date{\today}
\inventor{First Named Inventor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\tableofcontents
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\patentSection{Overview of the patent core topic}
%核心主题是干什么的，有什么用？此处的描述要尽可能的通俗易懂，专利的律师一般特别专业的技术是不明白的。
Describe the technical aspects of your idea in one to two paragraphs. Please provide:
\patentParagraph

\begin{enumerate}
	\item A high-level summary of the technical problem that your idea addresses. Usage scenarios or examples are helpful to provide context.
	\item A concise summary of how your idea is, or could be, implemented to solve the technical problem. The summary should focus on the improvements in software and/or hardware technology. If you have a white paper, architectural diagram, code flow diagram, or data flow diagram, please include that in the supporting document section below.
	\item A summary of the technical advantages of your idea. For example, how would your idea provide a new technical functionality or hardware feature, improvement in computational speed, reduction of needed resources, enhancement in security.
\end{enumerate}

\patentParagraph Objects of the Invention

\patentParagraph It is an object of this invention to \ldots Note that the objects should match the things that are needed as described in the last section. Do not describe the invention here, just the problems that will be solved or the utility of the invention.

\patentParagraph Still other objects and advantages of the invention will in part be obvious and will in part be apparent from the specification and drawings.

\patentParagraph Summary of the Invention

\patentParagraph In order to overcome \ldots, we do\ldots

\patentParagraph The invention accordingly comprises the several steps and the relation of one or more of such steps with respect to each of the others, and the apparatus embodying features of construction, combinations of elements and arrangement of parts that are adapted to affect such steps, all is exemplified in the following detailed disclosure, and the scope of the invention will be indicated in the claims.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\patentSection{Describe the technical differences}
%如果是发现我们已有的技术方案或者别人已有的技术方案存在某些问题促使我们设计新的技术方案的话，请写明存在的问题是什么，并最好描述出这个问题的产生原因。（需要注意的是，这里的问题一定是新技术方案针对性能解决的问题）。重点在于创新点，就是想要保护的点。此保护点要尽量的上位，已获得最大的利益。分析其他现存方案存在的不足。如有参考文献，请列出，便于代理的理解。
And any technical advantages of your solution over other solutions

Describe difference of your solution over other solutions and identify the innovative elements of your idea that should be protected.

\begin{enumerate}
	\item Based on your current knowledge, briefly describe existing solutions or products in the same technical field as your idea. No searching is needed.
	\item Summarize how your idea is technically different from these existing solutions or products. For example, describe how your software or hardware would differ and be superior in functionlity, operation, configueation, etc.
	\item Provide innovative elements of your idea that should be protected. Identify parts of your invention that a Microsoft competitor would want to implement.
	\item Supporting documentation. (File size limit is 125mb per attachment) Attach related documents to your idea - for example: specifications, diagrams, drawings, possibly related non-patent literature, etc. The following types are supported .avi, .doc, .docx, .gif, .htm, .html, .jpg, .jpeg, .mp4raw, .mpg, .msg, .one, oxps, .pdf, .png, .ppt, .pptx, .raw, .txt, .vsd, .vsdx, .wmv, .xls, .xlsx, .xps, .zip. File size limit is 125ml per attachment.
\end{enumerate}

\patentParagraph Background of the Invention

\patentParagraph Describe the past. Focus on problems that you will be solving. Talk about prior-art in detail to describe what has been done before and what the problems are. You are telling a story that inevitably leads up to ending statements like:

\patentParagraph What is needed is\ldots

\patentParagraph The things that are needed will be put forth as solutions in the next section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\patentSection{Detailed Description of the Preferred Embodiments}

\patentParagraph The details of the invention go here. I will use this area to make reference to the drawings so you can see how it's done.

\patentParagraph The arrangement in \referencePatentFigure{VisioDrawing} shows an exemplary arrangement of a preferred embodiment. In \referencePatentFigure{VisioDrawing}, one sees a \annotateWithName{Widget} and a \annotateWithName{Thing} with a preferable \annotateWithName{WidgetThingConnection} that enables the \annotateWithName{Thing} to process the data coming from the \annotateWithName{Widget}. I think you get the idea.  You can refer to the number as \annotationNumberReference{Widget} and if you need it underlined in a drawing, use \annotationNumberReferenceUnderlined{Widget}.

\patentParagraph You can either write: \annotateWithName{Thing} or you can write thing~\annotate{Thing}. They both produce the same thing.

\patentParagraph Note that you make and refer to equations like this:

\begin{equation}
E=mc^{2}\label{eq:energy}
\end{equation}

\patentParagraph One of my favorite equations is:

\begin{equation}
e^{j\theta}=\cos\left(\theta\right)+j\cdot\sin\left(\theta\right)\label{eq:euler}
\end{equation}

\patentParagraph We refer to the first equation as \prettyref{eq:energy} and the second as \prettyref{eq:euler}. The second equation \prettyref{eq:euler} is Euler's equation.

\patentParagraph It will thus be seen that the objects set forth above, among those made apparent from the preceding description, are efficiently attained and, because certain changes may be made in carrying out the above method and in the construction(s) set forth without departing from the spirit and scope of the invention, it is intended that all matter contained in the above description and shown in the accompanying drawings shall be interpreted as illustrative and not in a limiting sense.

\patentParagraph It is also to be understood that the following claims are intended to cover all of the generic and specific features of the invention herein described and all statements of the scope of the invention which, as a matter of language, might be said to fall therebetween.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\patentSection{Detailed Description of idea has been disclosed or used}

\patentParagraph 
\begin{enumerate}
	\item Has this idea been disclosed or will there be an upcoming disclosure outside of Microsoft without an obligation of confidentiality (e.g., not under NDA)?
	\item Has this idea been used commercially or is there a planned commercial use by Microsoft (e.g. shipped in a product or implemented in a cloud service)?
	\item What is the date of the first public disclosure/commercial use or anticipated disclosure/public use?
	\item Describe the disclosure.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\patentSection{Additional details you'd like to add?}

\patentParagraph

\begin{enumerate}
	\item What competitors are likely to implement your solution in the future? Please indicate competitors who will want to implement your idea and what aspects of your idea they will most want to copy.
	\item Why is your solution important to Microsoft? How will your idea give Microsoft a competitive advantage? How will it differentiate our products or services?
	\item What Microsoft Project, Product, Feature or Service is your idea likely to go into? What Microsoft products, Projects, Features, or services will your idea likely be implemented in now or in the future?

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\patentDrawingDescriptions
\patentDrawings
\end{document}
